### 2024-08-27 parts/correction.tex
moving polynomials to another section

\begin{corollary}
    \label{integer-binomial-polynomials:cor}
    Let $P \in \Rat[\vec{X}]$. Then, $P$ is a \kl{$\Rel$-rational polynomial}
    if and only if $P$ is an \kl{integer binomial polynomial}.
\end{corollary}
\begin{proof}
    Let $f = f_+ - f_-$ where both $f_+$ and $f_-$ are 
    \kl{star-free $\Nat$-polyregular functions}.
    One can apply \cref{n-sf-combinatorics:lem}
    to conclude that $P$ coincides with an 
    \kl{integer binomial polynomial} over large enough inputs,
    hence that $P$ is such a polynomial.
\end{proof}

>>>>

\begin{corollary}
    \label{integer-binomial-polynomials:cor}
    Let $P \in \Real[\vec{X}]$. Then, the following propreties are equivalent:
    \begin{enumerate}
        \item \label{int-bin-0:item} $P$ is an \kl{integer binomial polynomial},
        \item \label{int-bin-1:item} $P$ \kl{represented} by a \kl{star-free $\Nat$-polyregular function},
        \item \label{int-bin-2:item} $P(\Rel^k) \subseteq \Rel$.
    \end{enumerate}
\end{corollary}
\begin{proof}
    Let $f = f_+ - f_-$ where both $f_+$ and $f_-$ are 
    \kl{star-free $\Nat$-polyregular functions}.
    One can apply \cref{n-sf-combinatorics:lem}
    to conclude that $P$ coincides with an 
    \kl{integer binomial polynomial} over large enough inputs,
    hence that $P$ is such a polynomial.
\end{proof}
